Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-19 2016_ICML/cmrs.tex
Restructuring introduction of Section 3.

While information-based policies for Bayesian optimization such as ES and PES
have performed very well empirically, their internal objective of minimizing
the uncertainty in the location of the optimizer $\mathbf{x}^\star$, i.e.,
minimizing the differential entropy of $p_\star$, is actually different (albeit
related) to the common external objective of minimizing the simple regret of
$\mathbf{\tilde x}_N$, the recommendation of BO for $\mathbf{x}^\star$ after $N$
trials, where we define the simple regret of $\mathbf{\tilde x}_N$ as
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$.

Clearly, $\mathbf{x}^\star$ has zero and thus minimum simple regret, but a query that
results in the maximal decrease in $H(\mathbf{x}^\star)$ is not necessarily the
one that also results in the maximal decrease in the expected simple regret
as we will discuss in Section \ref{Section:MRS_Illustration}. In this section, we propose \emph{minimum
regret search} (MRS), which explicitly aims at minimizing the expected simple
regret.

>>>>

While information-based policies for Bayesian optimization such as ES and PES
have performed very well empirically, we discuss in Section \ref{Section:MRS_Illustration} 
that their internal objective of minimizing
the uncertainty in the location of the optimizer $\mathbf{x}^\star$, i.e.,
minimizing the differential entropy of $p_\star$, is actually different (albeit
related) to the common external objective of minimizing the simple regret of
$\mathbf{\tilde x}_N$, the recommendation of BO for $\mathbf{x}^\star$ after $N$
trials, where we define the simple regret of $\mathbf{\tilde x}_N$ as
$R_f(\mathbf{\tilde  x}_N) = f(\mathbf{x}^\star) - f(\mathbf{\tilde  x}_N) = \max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{\tilde x}_N)$.

Clearly, $\mathbf{x}^\star$ has zero and thus minimum simple regret, but a query that
results in the maximal decrease in $H(\mathbf{x}^\star)$ is not necessarily the
one that also results in the maximal decrease in the expected simple regret. 
In this section, we propose \emph{minimum regret search} (MRS), 
which explicitly aims at minimizing the expected simple
regret.
